---
title: "Module7_Group9"
author: "Nicole Wei"
date: "2023-11-19"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction
The force-length relationship of muscle function is directly related to actin-myosin overlap in sacromere -- the limited formation of crossbridges due to attachment range. The maximal isometric force produced is directlyed related to crossbridges formation. 
The human upper limb transect a lever system, but the ratio of mechanical advantage (MA) that predicts the amount of output transmitted by the input force emits a

in this study, we aim to investigate FL relationship within the human upper limb, particularly honing in on the forearm flexors and their response to eccentric fatigue:
  1) Does the isometric maximum voluntary contraction (MVC) force-angle data across the entire class align with a standard FL relationship, both in control and fatigued states?
  2) Is there a significant difference in the θmax between the FL relationships of the control and fatigue conditions?


Frame the questions, indicating why they are important, what background work has been done in this realm, and how you will answer them. Please include at least one reference to support the summary of previous work. Note: this can be done easily by refiguring the introduction to this project report.

## Methods

## Results
```{r cars}
summary(cars)
```

## Discussion

```{r pressure, echo=FALSE}
plot(pressure)
```

## Author Contribution

## References
Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
